{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2025-10-22 lagrangian.tex
Fixes for lecture 22.10.25

If a supersymmetric Lagrangian is to be invariant under an $U(1)_R$ transformation at all then a scalar superfield $\Phi$ must transform as
\begin{equation}
\Phi(x,\theta,\bar\theta)\to \Phi'(x,\theta',\bar\theta')= e^{ir_\Phi\alpha}\Phi(x,\theta, \bar\theta),
\end{equation}
where $r_\Phi$ is the charge of that superfield under the transformation, and $\alpha$ is the parameter of the transformation. The charge of a product of two superfields is then just the sum of the charges of the fields. This is required so that the kinetic term in the Lagrangian is invariant under the transformation.

We can then define the  transformation on the superspace coordinates as
\begin{equation}
\theta_A \to \theta_A' = e^{i\alpha} \theta_A, \quad \bar\theta_{\dot A} \to  \bar\theta'_{\dot A}= e^{-i\alpha} \bar\theta_{\dot A},
\end{equation}
where and the charge of $\theta$ and $\bar\theta$ under the transformation is 1 and $-1$, respectively. It follows from the differential representation of the supersymmetry generators (\ref{eq:diffrepQ}) and (\ref{eq:diffrepQbar}) that we must have
\begin{equation}
Q_A \to Q_A' = e^{-i\alpha} Q_A, \quad \bar Q_{\dot A} \to  \bar Q'_{\dot A}= e^{i\alpha} \bar Q_{\dot A}.
\end{equation}
This means that for a scalar (left- or right-handed) superfield the component fields $A$, $\psi$, and $F$ must transform as
\begin{equation}
A\to e^{ir_\Phi\alpha}A,\quad \psi\to e^{i(r_\Phi-1)\alpha} \psi,\quad F\to e^{i(r_\Phi-2)\alpha} F,
\end{equation}
while vector superfields must have zero $R$-charge since they are real, and their component fields, in the Wess--Zumino gauge must thus transform as
\begin{equation}
V_\mu \to V_\mu ,\quad \lambda \to e^{i\alpha} \lambda,\quad D\to D.
\end{equation}

>>>>

If a supersymmetric Lagrangian is to be invariant under a local $U(1)_R$ transformation at all then a scalar superfield $\Phi$ must transform as\footnote{Notice that this is not the same as a (super)gauge transformation in both that the transformation is local (not $x$-dependent), and there is an implicit generator $R$ here that does not commute with the $Q$s, because of the algebra relationship. The latter would not be the case for a supergauge transformation. It is only possible to have a local $R$-symmetry  with local supersymmetry transformations, {\it i.e.}\ $\delta_S=\alpha(x)Q+\bar\alpha(x)\bar Q$~\cite{Chamseddine:1995gb}.}
\begin{equation}
\Phi(x,\theta,\bar\theta)\to \Phi'(x,\theta',\bar\theta')= e^{ir_\Phi\alpha}\Phi(x,\theta, \bar\theta),
\end{equation}
where $r_\Phi$ is the charge of that superfield under the transformation, and $\alpha$ is the parameter of the tran.sformation. The charge of a product of two superfields is then just the sum of the charges of the fields. This is required so that the kinetic term in the Lagrangian is invariant under the transformation.

We can then define the  transformation on the superspace coordinates as
\begin{equation}
\theta_A \to \theta_A' = e^{i\alpha} \theta_A, \quad \bar\theta_{\dot A} \to  \bar\theta'_{\dot A}= e^{-i\alpha} \bar\theta_{\dot A},
\end{equation}
where the charge of $\theta$ and $\bar\theta$ under the transformation is 1 and $-1$, respectively. It follows from the differential representation of the supersymmetry generators (\ref{eq:diffrepQ}) and (\ref{eq:diffrepQbar}) that we must have
\begin{equation}
Q_A \to Q_A' = e^{-i\alpha} Q_A, \quad \bar Q_{\dot A} \to  \bar Q'_{\dot A}= e^{i\alpha} \bar Q_{\dot A}.
\end{equation}
This means that for a scalar (left- or right-handed) superfield the component fields $A$, $\psi$, and $F$ must transform as
\begin{equation}
A\to e^{ir_\Phi\alpha}A,\quad \psi\to e^{i(r_\Phi-1)\alpha} \psi,\quad F\to e^{i(r_\Phi-2)\alpha} F,
\end{equation}
while vector superfields must have zero $R$-charge since they are real, and their component fields, in the Wess--Zumino gauge must thus transform as
\begin{equation}
V_\mu \to V_\mu ,\quad \lambda \to e^{i\alpha} \lambda,\quad D\to D.
\end{equation}
